Trauma treatment delay

### 2023-11-29 manuscriptlongversion.Rmd
text

The 7,051 patients included in the first logistical regression had
characteristics as shown in table1. 69% of the individuals included were
men, with the remaining 31% being women. The mean value for the ISS
score was 11.30, with the standard deviation being 13.22. The majority
of the patients had General care department as their highest care level,
followed by ER, ICU, OR and lastly specialized care department. The
majority of patients, 82%, were not intubated during their stay in the
hospital, followed by 9.2% intubated at the hospital and 8.4% intubated
prehospitaly. The mean age of the patients was 44.95 years old, with a
standard deviation of 21.37. Most of the patients arrived during on-call
hour, 60%, with the rest arriving during working hours. 67% of the
patients arrived on a weekday, with the rest arriving on the weekend.

@@

In the following table, the results from the first regression analysis
is displayed.

The odds ratio is calculated, as well as a 95% confidence interval. The
p value is also shown.

As the table below shows, most of the variables, when adjusted for, does
not have an effect on the risk of receiving delayed treatment. Only when
not adjusted for, not being intubated had a correlation with increased
incidence of delayed treatment, while having higher ISS had the inverse
effect with lowering the rate of delayed treatment. Only two values in
one of the categories had an effect, having ICU or OR compared to having
ER as your highest care level. It suggests that patients who were in the
ICU or OR as their highest care level had a lower chance of receiving
delayed treatment compared with patients who had ER as their highest.

Below are the characteristics of the group used in the second logistical
regression. In this group, fewer patients had missing data, leading to
fewer exclusions. This resulted in different values in the same
variables as previously used in the first logistical regression. 68% of
the individuals included were men, with the remaining 32% being women.
The mean value for the ISS score was 10.07, with the standard deviation
being 10.27. The mean age of the patients was 44.20 years old, with a
standard deviation of 21.41. The majority of the patients had no
emergency measures performed, with 76% of the patients belonging to this
group. Following this, the most common emergency procedures were other
action, laparotomy, craniotomy, radiological intervention, intracranial
pressure measurement, and lastly, revascularization. The mean SBP was
137.60, with a standard deviation of 25.09. Mean respiratory rate was
18.59 with a standard deviation of 5.10. Lastly, mean GCS was 13.95,
with a standard deviation of 2.58.

![](table2.png)

@@

The analysis shows that when adjusted for, most variables do not have a
correlation with receiving delayed treatment. Three variables, ISS, RR
and GCS, had a correlation with receiving delayed treatment when not
adjusted for. However, when adjusted for, the correlation dissapeared.
In the case of emergency procedure, there was a correlation for all
emergency procedures performed and having a lowered incidence of delayed
treatment among the patients, compared with not receiving any emergency
measures performed.

![](results2.png)

>>>>

Below are the characteristics of the group used in the logistical
regression. Most of the patients were men, 68%, with that being a bit
higher in the delayed treatment group, 74%. The mean value for the ISS
score was 10.18, with that value being higher in the outcome group, at
16.81. The mean age of the patients was 45.18 years old, with it being
around the same in the delayed treatment group at 45.50. The mean number
of injuries among the delayed treatment patients was at 6.33, which is
higher than in the overall group at 4.76. The mean SBP was 137.33, with
a standard deviation of 25.69. Mean respiratory rate was 18.59 with it
being slightly higher in the outcome population at 20.39. Lastly, mean
GCS was 13.93, being lower among patients with delayed treatment at
12.56.

@@

@@

The analysis shows that when adjusted for, most variables do not have a
correlation with receiving delayed treatment. Three variables, ISS, RR
and GCS, had a correlation with receiving delayed treatment when not
adjusted for. However, when adjusted for, the correlation dissapeared.
In the case of emergency procedure, there was a correlation for all
emergency procedures performed and having a lowered incidence of delayed
treatment among the patients, compared with not receiving any emergency
measures performed
